The \dealii Library, Version 9.7

### 2025-08-21 9.7/paper.tex
End with a dot

\begin{quote}
%  authors removed:
%  Daniel       Arndt,
%  Wolfgang     Bangerth,
%  Maximilian   Bergbauer,
%  Bruno        Blais,
%  Marc         Fehling,
%  Rene         Gassmoeller,
%  Timo         Heister,
%  Luca         Heltai,
%  Martin       Kronbichler,
%  Matthias     Maier,
%  Peter        Munch,
%  Jean-Paul    Pelteret,
%  Sam          Scheuerman,
%  Bruno        Turcksin,
%  Siarhei      Uzunbajakau,
%  David        Wells,
%  Michał       Wichrowski,
Pasquale     Africa,
Henry        Arhin,
Alfredo      Buttari,
Bruna        Campos,
Nicholas     Cantrell,
Xiaoming     Cao,
Chayapol     Chaoveeraprasit,
Jerett       Cherry,
Dario        Coscia,
John         Coughlin,
Nikita       Daniliuk,
Crystal      Farris,
Marco        Feder,
Emmanuel     Ferdman,
Federico     Fernandez,
Olivier      Gaboriault,
Mohamad      Ghadban,
Mahdi        Gharehbaygloo,
Robin        Görmer,
Davit        Gyulamiryan,
Lóránt       Hadnagy,
Fernando     Herrera,
Robin        Hiniborch,
Quang        Hoang,
Jordan       Hoffart,
Sascha       Hofstetter,
Yimin        Jin,
Yann         Jobic,
Sean         Johnson,
Vaishnavi    Kale,
Sebastian    Kinnewig,
Andreas      Koch,
Jason        Landini,
Zhou         Lei,
Yingli       Li,
Nils         Margenberg,
Oreste       Marquis,
Ryan         Moulday,
Nils         Much,
Tileuzhan    Mukhamet,
Wasim~Niyaz  Munshi,
Natalia      Nebulishvili,
Luz          Paz,
David        Pecoraro,
Davide       Polverino,
Sanjeeb      Poudel,
Guilhem      Poy,
Laura        Prieto~Saavedra,
Sebastian    Proell,
Andreas      Ritthaler,
Mayank       Sabharwal,
Magdalena    Schreter,
Richard      Schussnig,
Kyle         Schwiebert,
Marc         Secanell,
Qingyuan     Shi,
Wyatt        Smith,
Simon        Sticko,
Dominik      Still,
Edward       Terrell,
Jan~Philipp  Thiele,
Xiaochuan    Tian,
Mikael       Vaillant,
Vinayak      Vijay,
Stephan      Voss,
Simon        Wiesheier,
Yi-Yung      Yang,
\end{quote}
Their contributions are much appreciated -- this project lives by its
community of users and contributors!

>>>>

\begin{quote}
%  authors removed:
%  Daniel       Arndt,
%  Wolfgang     Bangerth,
%  Maximilian   Bergbauer,
%  Bruno        Blais,
%  Marc         Fehling,
%  Rene         Gassmoeller,
%  Timo         Heister,
%  Luca         Heltai,
%  Martin       Kronbichler,
%  Matthias     Maier,
%  Peter        Munch,
%  Jean-Paul    Pelteret,
%  Sam          Scheuerman,
%  Bruno        Turcksin,
%  Siarhei      Uzunbajakau,
%  David        Wells,
%  Michał       Wichrowski,
Pasquale     Africa,
Henry        Arhin,
Alfredo      Buttari,
Bruna        Campos,
Nicholas     Cantrell,
Xiaoming     Cao,
Chayapol     Chaoveeraprasit,
Jerett       Cherry,
Dario        Coscia,
John         Coughlin,
Nikita       Daniliuk,
Crystal      Farris,
Marco        Feder,
Emmanuel     Ferdman,
Federico     Fernandez,
Olivier      Gaboriault,
Mohamad      Ghadban,
Mahdi        Gharehbaygloo,
Robin        Görmer,
Davit        Gyulamiryan,
Lóránt       Hadnagy,
Fernando     Herrera,
Robin        Hiniborch,
Quang        Hoang,
Jordan       Hoffart,
Sascha       Hofstetter,
Yimin        Jin,
Yann         Jobic,
Sean         Johnson,
Vaishnavi    Kale,
Sebastian    Kinnewig,
Andreas      Koch,
Jason        Landini,
Zhou         Lei,
Yingli       Li,
Nils         Margenberg,
Oreste       Marquis,
Ryan         Moulday,
Nils         Much,
Tileuzhan    Mukhamet,
Wasim~Niyaz  Munshi,
Natalia      Nebulishvili,
Luz          Paz,
David        Pecoraro,
Davide       Polverino,
Sanjeeb      Poudel,
Guilhem      Poy,
Laura        Prieto~Saavedra,
Sebastian    Proell,
Andreas      Ritthaler,
Mayank       Sabharwal,
Magdalena    Schreter,
Richard      Schussnig,
Kyle         Schwiebert,
Marc         Secanell,
Qingyuan     Shi,
Wyatt        Smith,
Simon        Sticko,
Dominik      Still,
Edward       Terrell,
Jan~Philipp  Thiele,
Xiaochuan    Tian,
Mikael       Vaillant,
Vinayak      Vijay,
Stephan      Voss,
Simon        Wiesheier,
Yi-Yung      Yang.
\end{quote}
Their contributions are much appreciated -- this project lives by its
community of users and contributors!
